---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Load packages
```{r}
library(ggplot2)
library(lme4)
library(tidyr)
```

## Load data

```{r}
# read CSV
data <- read.csv('data/strategic_signaling_data_long.csv')
```

## Mixed model analysis

### Political affiliation -> average perceived

```{r}
mdl_1 <- lmer(avg_perceived ~ poli_affil + (1 | tweet), data = data)
summary(mdl_1)
```

### Political affiliation -> average sentiment

```{r}
mdl_2 <- lmer(avg_sentiment ~ poli_affil + (1 | tweet), data = data)
summary(mdl_2)
```

## Results

Using a mixed-effects model above, we see that having a political affiliation of `right` (as opposed to `left`) is associated with an increased `avg_perceived` of 0.431 when accounting for tweet-level effects, and an increased `avg_sentiment` of 0.073, indicating a larger effect size on `avg_perceived`. We see similar amounts of error on the intercepts and effects. (I'll note that the first model, on `avg_perceived`, has a singular fit -- unusual, given how few parameters there are in the model -- and I'm not sure that there's something actually wrong here, so I'll continue.)

### Visualization

```{r}
datalong <- gather(data, key = 'avg', value='value', c('avg_perceived', 'avg_sentiment'))

ggplot(datalong, aes(x=poli_affil, y=value)) + 
  geom_bar(stat = 'summary', fun = "mean", fill = 'cadetblue') + 
  facet_wrap(~avg)
```

